\vspace{1.0cm} \LARGE \bf MERS-CoV spillover at the camel-human interface

### 2017-10-31 mers-structure.tex
Fix #27
Rephrase sentence about low Ne.

Despite lack of convergence, neither of the two demographic reconstructions show evidence of fluctuations in the relative genetic diversity ($N_e \tau$) of  MERS-CoV over time (Figure \ref{skygrid}).
We recover a similar demographic trajectory when estimating $N_{e}\tau$ over time with a skygrid tree prior across the genome split into ten fragments with independent phylogenetic trees to account for confounding effects of recombination (Figures \ref{skygrid}, \ref{skygrid_comparison}).
However, we do note that estimates of relative genetic diversity are relatively low overall with a mean estimate of $N_e\tau$ of 3.49 years (95\% HPD: 2.71--4.38), and consequently MERS-CoV phylogeny resembles a ladder often seen in human influenza A virus phylogenies \citep{bedford_strength_2011}.
This estimate of $N_e\tau$ can be translated into an estimate of effective prevalence $N_e$ given an estimate of generation time or serial intervals.
Given a 20 day duration of infection in camels \citep{adney_replication_2014}, we expect a 10 day serial interval or $\tau$ of 0.027 years per generation.
Dividing by $\tau$ yields an estimate of $N_e$ of 129 (100--162) individuals.

>>>>

Despite lack of convergence, neither of the two demographic reconstructions show evidence of fluctuations in the relative genetic diversity ($N_e \tau$) of  MERS-CoV over time (Figure \ref{skygrid}).
We recover a similar demographic trajectory when estimating $N_{e}\tau$ over time with a skygrid tree prior across the genome split into ten fragments with independent phylogenetic trees to account for confounding effects of recombination (Figures \ref{skygrid}, \ref{skygrid_comparison}).
However, we do note that coalescence rate estimates are high relative to the sampling time period, with a mean estimate of $N_e\tau$ at 3.49 years (95\% HPD: 2.71--4.38), and consequently MERS-CoV phylogeny resembles a ladder often seen in human influenza A virus phylogenies \citep{bedford_strength_2011}.
This estimate of $N_e\tau$ can be translated into an estimate of effective prevalence $N_e$ given an estimate of generation time or serial intervals.
Given a 20 day duration of infection in camels \citep{adney_replication_2014}, we expect a 10 day serial interval or $\tau$ of 0.027 years per generation.
Dividing by $\tau$ yields an estimate of $N_e$ of 129 (100--162) individuals.
